% EOD Documentation Paper #3
% Project initiated Dec 22 2013

%\documentclass{emulateapj}
% Requirement of PASP to use preprint and aastex
\documentclass[11pt,preprint]{aastex}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj} 
\usepackage{epstopdf}  
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

\usepackage{CJK} 

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}
\def\rearth{R_\oplus}


\maxdeadcycles=1000 % need this to have bunch of figures on each page
                    % at end

\slugcomment{}
\shorttitle{}
\shortauthors{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{CJK*}{UTF8}{gbsn}

\title{Updates on the Exoplanet Orbit Database}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ying Feng\altaffilmark{1,2}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{Onsi Fakhouri}
\author{and Friends}

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to datamaster@exoplanets.org.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Make sure to mention: data are available at exoplanets.org; KOIs are included.
\end{abstract}  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014 (exoplanets.org). \kepler\ contributed to a vast
majority of these new discoveries ($> 800$) while providing an
additional sample of over 3000 exoplanet candidates(\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has
surpassed the radial velocity (RV) method and become the most fruitful
mean for detecting exoplanets. Meanwhile, great promises lie within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).

% The business of tracking planet discoveries and EOD
This paper describes the continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
and the Exoplanets Data Explorer to keep track of the exoplanet
discoveries and catalog their orbital parameters and host star
properties. There are also other entities devoted to this effort,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011}, the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

% data access and popularity
The EOD is hosted by exoplanets.org, which also hosts the Exoplanets
Data Explorer, an interactive table with plotting tools including all
the EOD exoplanets as well as other confirmed exoplanets (and now also
KOIs). The entire dataset of exoplanets.org is available for download
as a single {\tt .csv} file at the website's front page.\footnote{At
  \url{exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
used in exoplanet researches (e.g., \citealt{Dawson2013},
\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
\citealt{Weiss2014}), and the website exoplanets.org is among the most
visited exoplanet databases, with over $47,000$ visitors in 2013
according to Google Analytics.

% updates on EOD and the website
Since \cite{Wright2011}, the EOD has expanded its scope and we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It has also ingested more
parameters of the exoplanet systems and host stars, and some
parameters are revised or deleted. We describe the updates with the
EOD in Section~\ref{sec:update}. We also describe the updates to the
hosting website, exoplanets.org. The Exoplanet Data Explorer at
exoplanets.org has expanded its scope and now includes the
\kepler\ exoplanet candidates (KOIs). We describe these changes in
Section~\ref{sec:kepler}. The website has also gone through major
back-end changes since \cite{Wright2011}, which is described in
Section~\ref{sec:website}.

%------------------------------------------------------------------
% RECYCLE BIN
\begin{comment}
Since the first peer-reviewed list of exoplanets with robust orbits
\citep{Butler2002,Butler2006}, the count of exoplanets has increased
from less than 200 to over 1490 as of March 2014
(exoplanets.org). Before the launch of NASA's \kepler\ mission
\citep{Borucki2010}, most confirmed exoplanets were discovered via the
precise radial velocity (RV) method. However, since 2009, \kepler\ has
contributed over $\sim$ 800 confirmed exoplanets (e.g.,
\ciatealt{Marcy2014}, \citealt{Rowe2014}) as well as over 3000
exoplanet candidates (\kepler\ Objects of Interest, KOIs;
e.g.~\citealt{Batalha2013}).

As the number of exoplanet discoveries keeps rising, it is important
to keep track of these discoveries and cataloging the orbital
parameters and host star properties of exoplanet systems. There are
several entities that are devoted to this effort, including the
Exoplanet Orbit Database (EOD) and Exoplanets Data Explorer\footnote{See
  \url{http://exoplanets.org}.} \citep{Wright2011}, the Extrasolar
Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}, and so on.

This paper describes the continuing efforts since \cite{Wright2011} to
maintain the EOD and the Exoplanets Data Explorer at exoplanets.org.

The efforts of keeping track of exoplanet discoveries are being
carried out by several entities, and most notably, the Extrasolar
Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}, and the Exoplanet Orbit Database (EOD) and
Exoplanets Data Explorer\footnote{See \url{http://exoplanets.org}.}
\citep{Wright2011}.
\end{comment}
%------------------------------------------------------------------


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}
Make sure to cite \cite{Wright2013} for the definition of orbital elements. 

Scope of EOD has changed in the following ways:

1. Definition of planets: not strictly smaller than 24 \mjup\ any
more? Or still true? We still require smaller than 24 \mjup.

2. Host stars: not only `normal stars' any more? Not any more -
neutron stars are there (at least)! This requirement is completely gone.

3. Change on definition of `well-determined' orbital parameters? No. Still
qualitative, still the same as described in Section~2 of \cite{Wright2011}.

4. Inclusion of planets discovered beyond RV and transit.

Purposes of EOD have not changed?

We only describe new additions and revised fields here, but list all
fields. For details on other fields, see \cite{Wright2011}. We divide
the fields into categories in consistency with the interactive table
on exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}} Make a note
here that though we focus on EOD in this Section, the fields apply to
all planets on exoplanets.org.

%------------------------------------------------------------------------------
\subsection{Discovery and References}

We report general information of when, by whom and how the planets
were discovered and provide the references. We describe the added
fields since \cite{Wright2011} below.

{\bf KEPID} stands for KEPler ID which is the integer number assigned
for a Kepler host star. KEPID is only available for the unconfirmed
KOI which we import directly from the Exoplanet Archive. Therefore,
none of the EOD planets and the confirmed Kepler planets has KEPID.

{\bf KOI} stands for Kepler Objects of Interest which is a star with
transit signals detected by \kepler\ but have not been confirmed to
due to exoplanets. The KOI field contains a floating point number that
consist of a whole number designated to the host star followed by a
decimal number denoting a candidate planet. For example, KOI 102 is a
star suspected to host two exoplanets and KOI 102.01 is the inner
planet candidate and KOI 102.02 is the outer one. Once a candidate is
confirmed, the NAME field of the planet is replaced by the official
\kepler\ ID ('Kepler' followed by a hyphen, an integer and a
letter). The KOI number is used as OTHERNAME. None of the KOIs are in
the EOD and for more information see Section~\ref{sec:kepler}.

\begin{comment}
\textit {Sharon: you need to say what KOI stores. When writing each
  field, keep in mind you need to cover the following so that the
  reader will completely understand: (1) what the field stands for
  (e.g., in case of an abbreviation like KOI); (2) what the field
  physically means, like `KOI' means planet candidates that have
  transit signals as detected by \kepler\ but have not been confirmed,
  and make sure to be thorough at what you say -- sometimes things are
  not that obvious to an outsider reader, e.g., think if a cosmologist
  would understand what you're saying when reading it; (3) what the
  field actually contains, e.g. KOI contains the KOI number designated
  by the \kepler\ team (right?), it is a floating point number, and
  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
  something...; (4) why we added this new field, if this information
  is helpful, or if it's a revised field since \cite{Wright2011}, what
  is changed. Also, use \kepler\ (which is a defined symbol in our
  ms.tex file), instead of typing out Kepler, since you need italic.
  Don't be afraid to write more! Being concise is important, but it's
  always easier to trim down things than to add things on, especially
  for a documentation type of paper like this. Let's be thorough at
  first, then try to reach optimal conciseness.}
 \end{comment}

KDE: obselete field! Detele from the table.

{\bf EOD} is a flag which indicates whether an exoplanet has
well-characterized orbital parameters (e.g. period (PER)). EOD equals
1 means the exoplanet is in the EOD. We added this field because
exoplanets.org now also includes robustly discovered planets that do
not have well-characterized orbits, and also \kepler\ planet
candidates (see Section~\ref{sec:kepler} for more details).

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
indicate that a planet detected via theses methods. For example,
MICROLENSING $=$ 1 means the planet is detected by a microlensing
event. However, we require the detection to be robust, as determined
by the QUAlity Control Board of the Exoplanet Database, QUACBED.


%------------------------------------------------------------------------------
\subsection{Orbital Parameters}
We report the orbital parameters that determine the shape of the
planet's orbit. Depending on the detection methods, different sets of
parameters are given by the literatures. For instance, if a planet is
detected by the radial velocity method, the semiamplitude, $K$, is
reported whereas the inclination of the orbit, $i$, is reported by the
transit method. We describe the added fields since \cite{Wright2011}
below.  

{\bf MASS} is the mass of the planet in the unit of Jupiter
mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
MSINI) of the planets. We now report the mass as well when it is
available. For example, if a planet is discovered by microlensing, we
report the actual mass of the planet according to the literature. If a
planet has both radial velocity and transit measurements, we calculate
the mass from the minimum mass and the orbital inclination. MASS is
set to MSINI if the orbital inclination is not given and the MASSREF
is set to ``Set to MSINI; I unknown''.  

ZZZ For KOIs without MSINI measured, we calculate their mass using the
mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use
\cite{Lissauer2011}, and for KOIs with $6\rearth<R<17\rearth$ we use
\cite{Mordasini2012}.  

{\bf SEP} is the projected separation on the sky between the host star
and the planet in the unit of AU. For directly imaged planets, the
literatures give the projected separation and we report this value.
If SEP is not directly measured but the semi-major (A) is available,
then SEP is set to A with the reference ``Set to A''. For the cases
where only the projected separation is given such as imaged planets,
then the semi-major axis is set to SEP.

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the
unit of degree and for now this is only measured for some of the
directly imaged planets, which are not in the EOD.


%------------------------------------------------------------------------------
\subsection{Transit Parameters}
We report the transit parameters, which are available only when the
planet has TRANSIT flag equal to 1. We describe added fields since
\cite{Wright2011} below.

{\bf DR} is the distance between the planet and the star during the
transit in stellar radii. This is one of the parameters that goes into
the transit light curve modeling (see e.g. \citealt{Batalha2013}).

{\bf RR} is the ratio of the planetary radius and the stellar
radius. If the transit depth (DEPTH) is not given, we calculate DEPTH
by taking square of RR but we do not calculate RR from DEPTH.


%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}

We have added an entirely new set of fields for the secondary
eclipse. Previously, due to the limits of instrumentation, there were
not much available measured secondary eclipse depths. Since
\cite{Wright2011}, as many different surveys have been launched,
secondary eclipse depths at multiple bands are now
available. Therefore, we added this entire new set of fields since.

{\bf SE} flag indicates whether the system has detected secondary
eclipse in any of the two Micron All-Sky Survey (2MASS;
\citealt{Skrustskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
and 4 Spitzer IRAC bands. SE is a boolean and being true indicates the
system has at least one detected secondary eclipse.

{\bf SEDEPTHX} whereas X stands for one of J H KS KP 36 45 58 80:
these fields are the secondary eclipse depth measured in the
corresponding wavelength band. SEDEPTHJ, H, and KS are the depths
measured in the 2MASS wavelength band in near infrared each centered
at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively. KP is
the depth measured in the \kepler\ photometry band which ranges from
400 to 865~nm. The rest four stand for the Spitzer bands centered at
3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.

{\bf SET} is the epoch of secondary eclipse center in HJD.

%------------------------------------------------------------------------------
\subsection{Stellar Properties}
This set of parameters is to provide users the physical parameters of
the exoplanet host stars.  Most of the parameters are derived from the
stellar models in the literatures and we provide the readers with the
references. We describe added fields since \cite{Wright2011} below.

{\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of
the planetary system and is reported in km/s.

{\bf RSTAR} is the radius of the star in the solar radius.

{\bf RHOSTAR} is the density of the star in the unit of g/cm$^3$.

%------------------------------------------------------------------------------
\subsection {Stellar Magnitudes}

We provide the brightness of the host star measured in different
wavelengths. We report optical magnitudes ($V$ and $B-V$), 2MASS $J$,
$H$, and $K_s$ magnitudes and we added {\bf KP} since
\cite{Wright2011}, which is the stellar magnitude measured through the
Kepler bandpass.

%------------------------------------------------------------------------------
\subsection{Coordinates and Catalogs}
We report the coordinates of the host star as well as the stellar ID
as designated by different catalogs.  We added {\bf DIST} since
\cite{Wright2011}, which is the distance of the host star in the unit
of pc. If only parallax (PAR) is given, we convert it to DIST and vice
versa. If the literature does not report DIST or PAR, then we obtain
PAR from the Hipparcos data set by \cite{van Leeuwen2009}.

%------------------------------------------------------------------------------
\subsection{Uncertainties}

We now report uncertainties for a certain field X as XUPPER, XLOWER
and UX. XUPPER and XLOWER store the upper and lower 1$\sigma$
uncertainties, and they are different when the error bars are
asymmetric. UX contains the 1$\sigma$ uncertainty, and it
equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
bars. Fields that have XUPPER, XLOWER and UX are: (list of fields).

%------------------------------------------------------------------------------
\subsection{References}

The fields {\bf XREF} and {\bf XURL} store the peer-reviewed reference and link to
the publication for the field X. 

Added field: MONTH, PLANETDISCMETH, STARDISCMETH.
The following fields now have XREF and XURL: (previously in
\cite{Wright2011}) DIST, TRANSIT, BINARY; (new) fields in stellar
parameters: V, VSINI, GAMMA; all orbit pars except for trend and
freeze\_ecc; all transit parameters; all SE parameters; fields for
stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE. 

VREF is not the same as REF for J H KS, which do not have XREF
fields. See \cite{Wright2011} for references of J H KS mags -- I think
he mentioned it there.

Other general reference fields: In \cite{Wright2011}: FIRSTREF,
FIRSTURL, ORBREF, ORBURL. New: SPECREF, SPECURL contain source of most
of the spectroscopic parameters listed for convenience; actual
references in the REF fields take precedence over this one.

{\bf MONTH} field reports an integer of the month when the
peer-reviewed paper is accepted to the ApJ to better track of the
trend in the exoplanet detections.

{\bf PLANETDISCMENT} and {\bf STARDISCMETH} are the fields that report
the discovery methods for the host star and the planet See Section~
for more details.


%------------------------------------------------------------------------------
\subsection{Revised and Removed Fields}
We have major updates by taking out some of the fields and by revising the existing fields. Here, we explain why we removed or revised such fields. 

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by ZZZ Rossiter-McLaughlin
effect. $\lambda$ is introduced because the true spin-orbit angle
($\phi$), defined as the angle between the stellar spin axis and the
orbital axis, is normally not directly measurable. We follow the
definition of $\lambda$ in Fabrycky and Winn 2009 where the
coordinates are defined as follows; the $z$-axis points toward the
observer, the $x$-axis points along the intersection of the sky plane
and the planet's orbital plane with the ascending node of the planet
having $x<0$, and the $y$-axis completes a right
handed-triad. $\lambda$ is measured clockwise on the sky from the
$y$-axis to the projected stellar rotational axis. Some literatures
report $\beta = -\lambda$ instead. We sorted these cases out and made
sure that our $\lambda$'s are following the definition of Fabrycky and
Winn 2009.

{\bf I} is the orbital inclination. This field is not newly added but
we chose to describe it here since our database now has the
inclination for planets detected by methods other than
transit. Previously, only transiting systems used to have the
inclination measured. However, now sometimes for non-transiting
systems the values of I are also available. For instance, if the
system was first detected by radial velocity and has a follow-up
transit observation, then the inclination can be measured. To sum up,
all the transiting planets have measured orbital inclination and
currently, we also have one microlensing planet with measured
inclination. *** give the example!


{\bf OTHERNAME} - This is now listed as other name of planet instead
of star; ** OTHTERNAME has always been the name of the star I
think...?

{\bf DISCMETH} field previously reported the mouthed of discovery,
which was either radial velocity or transit. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and {\bf STARDISCMETH} to better report how
the host star and the planet are detected. Furthermore, they now have
value of one of the following: radial velocity, transit, imaging,
microlensing, timing, or astrometry.

{\bf S} field previously reported the Mount Wilson Ca II S-value and
now it is changed to SHK.  ; ZZZ What's the source for SHK and RHK?
Still discovery paper and Butler 2006? ZZZ SHK is a poorly maintained
field, and it is unreferenced at the moment though we plan to include
proper reference in the future.

{\bf SPSTAR} field previously reported the stellar type of the host
star. We choose to remove this field because....? - stellar type of
star (unvetted), gone;

{\bf NSTEDID} field reported ID of host star in NStED and now it is
replaced by EANAME, which is the name of the star as appears on the
Exoplanet Archive.

{\bf MASSREF} and {\bf MASSURL} fields were used to report the
reference and the url of stellar mass but now they are used for planet
mass.

%------------------------------------------------------------------------------
Figure: Figure of single planet page, to show updated transit
parameters and RV curves etc.?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}

Since \cite{Wright2011}, as more planets were discovered by different
methods other than radial velocity and transit, we have expanded this
information to better ingest those planets into our database.

Planets primarily detected by these methods do not have robust orbital
parameters, they are categorized as ``Other Planets'' on
exoplanets.org.

If planets have follow up radial velocity or transit observations and
thus have good orbital parameters, they have EOD flags. See
Section~\ref{sec:kepler} for more information about `Other Planets'.


We now include \kepler\ candidates... They can be displayed by
checking the `Kepler' option for the interactive data table.

We also include robustly detected planets discovered microlensing,
imaging, timing, astrometric motion. They can be displayed by check
the `Other' option for the table. They are not included in the EOD
(especially some microlensing and imaging planets) because of poorly
characterized orbits...

Also add our criteria for vetting IMAGING planets, which can be found
here: http://exoplanets.org/methodology.html; do we have any similar
criteria for Microlensing, timing and astrometry planets? Like mass
cut etc.?

Figure: some comparison figures of Kepler candidate properties
vs. EOD planet properties, such as mass-period, mass-radius?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the Website}\label{sec:website}

Onsi? Essential updates on the website.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future}\label{sec:conclusion}

Any planned future improvements and updates?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments

NSF funding?

SXW acknowledges support from PSARC.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References:
%\newpage
\input{references.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table
\clearpage

\begin{deluxetable}{llll}
\tabletypesize{\scriptsize}
%\rotate
\tablewidth{0pt}
\tablecaption{Fields of Exoplanet Orbit Database\label{tab:par}}
\tablehead{
  \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{b}}
}
\startdata
%
\sidehead{\textbf{Planet Information}}
NAME\dotfill & String & Name of planet & \nodata \\
OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\
COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
HD\dotfill & Long Integer & Henry Draper number of sar & \nodata \\
HR\dotfill & Integer & Bright Star Catalog number of star & \nodata \\
HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of
star & \nodata \\
SAO\dotfill & Long Integer & SAO catalog number of star & \nodata \\
GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata \\
BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata \\
RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  \\
DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata \\
DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
KEPID\dotfill & Long Integer & The unique \kepler\ star identifier & \nodata \\
KOI\dotfill & Float & KOI object number & \nodata \\
KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\
%
\sidehead{\textbf{Stellar Parameters}}
BMV\dotfill & Float & $B-V$ color & \nodata \\
V\dotfill & Float & $V$ magnitude & -REF,-URL \\
J\dotfill & Float & $J$ magnitude & \nodata \\
H\dotfill & Float & $H$ magnitude & \nodata \\
KS\dotfill & Float & $K_S$ magnitude & \nodata \\
DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. \\
PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
VSINI\dotfill & Float & Projected equatorial rotational velocity of
star in k\mps & -UPPER, etc. \\
GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. \\
%
\sidehead{\textbf{Orbit Parameters}}
PER\dotfill & Double & Orbital period in days & -UPPER, etc. \\
ECC\dotfill & Float & Orbital eccentricity & -UPPER, etc. \\
OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. \\
K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER, etc. \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\
I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. \\
MSINI\dotfill & Float & Minimum mass (as calculated from the mass
function) in \mjup & -UPPER, etc. \\
A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. \\
SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. \\
TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
LAMBDA\dotfill & Float & Projected spin-orbit misalignment in degrees & -UPPER, etc. \\
BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. \\
FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\
%
\sidehead{\textbf{Transit Parameters}}
DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\
TT\dotfill & Float & Epoch of transit center in
HJD\tablenotemark{d} & -UPPER, etc. \\
R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER, etc. \\
AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. \\
B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &
-UPPER, etc. \\
GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of planet in cgs unit &
-UPPER, etc. \\
TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\
DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. \\
RR\dotfill & Float & $(R_p/R_*)$ & -UPPER, etc. \\
%
\sidehead{\textbf{Secondary Eclipse}}
SE\dotfill & Boolean & If true, at least one secondary eclipse has
been detected & -REF,-URL \\
SEDEPTHJ\dotfill & Float & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
SEDEPTHH\dotfill & Float & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
SEDEPTHKS\dotfill & Float & Secondary eclipse depth in $K_S$
band & -UPPER, etc. \\
SEDEPTHKP\dotfill & Float & Secondary eclipse depth in the
\kepler\ photometry band & -UPPER, etc. \\
SEDEPTH36\dotfill & Float & Secondary eclipse depth in
\spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. \\
SEDEPTH45\dotfill & Float & Secondary eclipse depth in
\spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. \\
SEDEPTH58\dotfill & Float & Secondary eclipse depth in
\spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. \\
SEDEPTH80\dotfill & Float & Secondary eclipse depth in
\spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\
SET\dotfill & Double & Epoch of secondary eclipse center in
HJD\tablenotemark{d} & -UPPER, etc. \\
%
\sidehead{\textbf{Fit \& References}}
RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \nodata \\
CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata \\
NOBS\dotfill & Integer & Number of observations used in fit & \nodata \\
NCOMP\dotfill & Integer & Number of planetary companions known & \nodata \\
MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
FIRSTREF\dotfill & String & First peer-reviewed publication of
planetary orbit & FIRSTURL \\
ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
%
\sidehead{\textbf{Stellar Properties}}
STAR\dotfill & String & Standard name for host star & \nodata \\
MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. \\
LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
host star in cgs unit & -UPPER, etc. \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata \\
SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL \\
%
\sidehead{\textbf{Links}}
JSNAME\dotfill & String & Name of host star used in the Extrasolar
Planets Encyclopaedia & EPEURL \\
ETDNAME\dotfill & String & Name of planet used in the Exoplanet
Transit Database & ETDURL \\
SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
planet, if available) & SIMBADURL \\
EANAME\dotfill & String & Name of planet used in the Exoplanet
Archive database & EAURL \\
\enddata
\tablenotetext{a}{Fields in bold are updates or new additions from
  \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
\tablenotetext{b}{-UPPER etc. means ``-UPPER, -LOWER, U-, -REF, -URL",
where ``-" stands for the name of the field listed in the first
column. They are...}
\tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};
  changed to other commonly used name for planet.}
\tablenotetext{d}{The same as in \cite{Wright2011}, HJD/BJD etc.\ are
  still not consistent.}
\end{deluxetable}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{CJK*}

\end{document}
