% EOD Documentation Paper #3
% Project initiated Dec 22 2013

%\documentclass{emulateapj}
% Requirement of PASP to use preprint and aastex
\documentclass[11pt,preprint]{aastex}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj} 
\usepackage{epstopdf}  
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

\usepackage{CJK} 

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}


\maxdeadcycles=1000 % need this to have bunch of figures on each page
                    % at end

\slugcomment{}
\shorttitle{}
\shortauthors{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{CJK*}{UTF8}{gbsn}

\title{Updates on the Exoplanet Orbit Database}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ying Feng\altaffilmark{1,2}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{Onsi Fakhouri}
\author{and Friends}

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to datamaster@exoplanets.org.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\end{abstract}  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

Recent development of exoplanet discoveries, especially
\kepler\ discoveries.

The business of keeping track of exoplanet discoveries, where EOD
stands, and a brief history of EOD.

What this paper is about: an update on EOD and the services our
website, exoplanets.org, provide.

According to Google Analytics, $47,000$ people visited exoplanets.org
in 2013.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}

Scope of EOD has changed in the following ways:

1. Definition of planets: not strictly smaller than 24 \mjup\ any
more? Or still true? We still require smaller than 24 \mjup.

2. Host stars: not only `normal stars' any more? Not any more -
neutron stars are there (at least)! This requirement is completely gone.

3. Change on definition of `well-determined' orbital parameters? No. Still
qualitative, still the same as described in Section~2 of \cite{Wright2011}.

4. Inclusion of planets discovered beyond RV and transit.

Purposes of EOD have not changed?

We only describe new additions and revised fields here, but list all
fields. For details on other fields, see \cite{Wright2011}. We divide
the fields into categories in consistency with the interactive table
on exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}} Make a note
here that though we focus on EOD in this Section, the fields apply to
all planets on exoplanets.org.

%------------------------------------------------------------------------------
\subsection{Planet Information}

We report basic planet information to give our users general
information of when, by whom and how the planets were
discovered. Since \cite{Wright2011}, as more planets were discovered
by different methods other than radial velocity and transit, we have
expanded this information to better ingest those planets into our
database.

Added fields since \cite{Wright2011}:

\textit{Sharon: I don't think the first sentence is true... Looking at
  the fields in the Planet Information section in the table, it
  doesn't contain when who or how at all... The current way of
  dividing fields into these categories is a bit weird, but we are
  definitely not changing it in our paper or change the website any
  time soon... I'm guessing you want to summarize what Planet
  Information fields cover in the first sentence here, so maybe look
  at the table and give a very general summary of what those fields
  are.
  I'm not sure what's the purpose of the second sentence... It sounds
  like something we generally did for EOD. Maybe we should move it to
  the paragraph above in the overview text for
  Section~\ref{sec:update}. Think more about what the purpose of the
  subsection overview should serve.}


KEPID: None of EOD planets has KEPID! This is just something we copied
from Exoplanet Archive...


KOI: KOI represents `Kepler Objects of Interest' which is a star suspected to host transiting exoplanet. Transit signals are detected by \kepler\ but have not been confirmed to be planets. KOI field contains floating points that is consisted of a whole number designated to the host star followed by a decimal number denoting candidate planets. For example, KOI 102 is a star suspected to host multiple exoplanets and KOI 102.01 is an inner and KOI 102.02 is an outer planet candidate. Once the candidates are confirmed to be planets, the host star is designated \kepler\ followed by a hyphen and an integer. 
\textit {I am not actually sure why we started reporting KOI numbers... maybe to better track of exoplanets?}

\textit {Sharon: you need to say what KOI stores. When writing each
  field, keep in mind you need to cover the following so that the
  reader will completely understand: (1) what the field stands for
  (e.g., in case of an abbreviation like KOI); (2) what the field
  physically means, like `KOI' means planet candidates that have transit
  signals as detected by \kepler\ but have not been confirmed, and
  make sure to be thorough at what you say -- sometimes things are not
  that obvious to an outsider reader, e.g., think if a cosmologist
  would understand what you're saying when reading it; (3) what the
  field actually contains, e.g. KOI contains the KOI number designated
  by the \kepler\ team (right?), it is a floating point number, and
  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
  something...; (4) why we added this new field, if this information
  is helpful, or if it's a revised field since \cite{Wright2011}, what
  is changed. Also, use \kepler\ (which is a defined symbol in our ms.tex file),
  instead of typing out Kepler, since you need italic.
  Don't be afraid to write more! Being concise is important, but it's
  always easier to trim down things than to add things on, especially
  for a documentation type of paper like this. Let's be thorough at
  first, then try to reach optimal conciseness.}

KDE: obselete field! Detele from the table.

EOD: EOD flag indicates planets with good Keplerian orbits. They have
robust orbital parameters such as PER, ECC, K, OM, and I. 

EOD: A planet with the EOD flag being true indicates that it has
well-characterized orbital parameters such as PER, ECC, K, OM, and I
and is thus included in the EOD. We added this field because
exoplanets.org now also includes robustly discovered planets that do
not have well-characterized orbits, and also \kepler\ planet
candidates (see Section~\ref{sec:kepler} for more details).

\textit {Sharon: I've provided my version here: the stuff I added on
  top of your writing is what I think was missing and may make a
  cosmologist wonder. ;)
  Also, EOD doesn't require the orbit to be 'Keplerian', right? We do
  include reported dynamic fits - they're definitely not
  Keplerian. Am I right?
  Note that I've covered all the 4 aspects I mentioned above. :)}

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
ING, IMAGING, TIMING and ASTROMETRY fields for planets detected by
methods other than radial velocity and transit. Since planets detected
by these methods do not have robust orbital parameters, they are
categorized as ``Other Planets'' on exoplanets.org. However, if
planets have follow up radial velocity or transit observations and
thus have good orbital parameters, they have EOD flags. See
Section~\ref{sec:kepler} for more information about `Other Planets'. 

\textit {Sharon: you've changed `discovered' to `detected', but it's
  still not an accurate description. Let's meet and discuss this in
  person. 
  old: Sharon's
  comments: Instead of saying `discovered', we should say `detected'
  -- some planets are detected by these methods but are not
  necessarily discovered by them at the first place. Re-phrase the
  last sentence -- not all of planets with any of these TRUE are in
  `Other Planets', only some are, so maybe just note planets
  discovered by these methods are not necessarily in EOD and direct
  the reader to Section~\ref{sec:kepler} where we talk about `Other
  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
  updates though the fields apply to all planets on
  exoplanets.org. Need to note here that we require the detection to
  be robust, as determined by the QUAlity Control Board of the
  Exoplanet Database, QUACBED.}


%------------------------------------------------------------------------------
\subsection{Stellar Parameters}
Stellar parameters section is consisted of 3 parts: Stellar properties, Stellar magnitudes, and Coordinates and Catalog. This section is to provide our users detailed information about the exoplanet hosting stars. Stellar properties section contains name, mass, and consistent set of metalicities (FE) , effective temperature (TEFF), surface gravity (LOGG), projected rotational velocity (VSINI), and the systematic radial velocity (GAMMA). Stellar magnitudes section includes optical magnitudes of the star (V and BMV) as well as 2MASS infrared (J, H, and K) and Kepler bandpass magnitude (KP). Coordinates and Catalog section includes the right ascension (RA) and the declination (DEC) of the host star, parallax (PAR) and distance (DIST) and the integers designated by different catalogs. 

Added fields since \cite{Wright2011}:

DIST is the distance of the host star in the unit of pc. It sometimes is calculated from the parallax that come from the Hipparcos data set by van Leeuwen (200).

GAMMA is the newly added field under Stellar properties. It is the radial velocity of the center of mass of the planetary system and is reported in km/s.  

ZZZ KP added?

%------------------------------------------------------------------------------
\subsection{Orbit Parameters}

Added fields since \cite{Wright2011}:


MASS: Previously, we only reported the minimum mass (MSINI) of the
planets. We now report mass of the planet in the unit of Jupiter
mass. If a planet is discovered by transit, the planet mass is given
by the literature. However, if a planet is detected by radial velocity
method, the minimum mass is given in which case we calculate the mass
by dividing the minimum mass by the orbit inclination. MASS is set to
MSINI if the orbital inclination is not given and the MASSREF is set
to ``Set to MSINI; I unknown''. 

MASS: For KOIs without MSINI measured, Exoplanet Archive reports MASS
based on converting radius into mass.


SEP

BIGOM

LAMBDA: the literature has conflicted definitions of LAMBDA, and we
sorted it out and made sure it is consistent in EOD.

LAMBDA: We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009. 

I: it used to be for transit systems only. Now sometimes for
non-transiting systems the values of I are also available.

%------------------------------------------------------------------------------
\subsection{Transit Parameters}

Added fields since \cite{Wright2011}:

DR

RR

%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}

This is a entire new set of fields since \cite{Wright2011}:

SE

SEDEPTH J H KS KP 36 45 58 80

SET

%------------------------------------------------------------------------------
\subsection{Stellar Properties}

Difference from Stellar Parameters: these are derived parameters based
on spectroscopy and stellar models.
Added fields since \cite{Wright2011}:

RSTAR

RHOSTAR

KP

%------------------------------------------------------------------------------
\subsection{Uncertainties}

We now report uncertainties for a certain field X as XUPPER, XLOWER
and UX. XUPPER and XLOWER store the upper and lower 1$\sigma$
uncertainties, and they are different when the error bars are
asymmetric. UX contains the 1$\sigma$ uncertainty, and it
equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
bars. Fields that have XUPPER, XLOWER and UX are: (list of fields).

%------------------------------------------------------------------------------
\subsection{References}

Added field: MONTH, PLANETDISCMETH, STARDISCMETH.

The fields XREF and XURL store the peer-reviewed reference and link to
the publication for the field X. The following fields now have XREF
and XURL: (previously in \citealt{Wright2011}) DIST, TRANSIT, BINARY;
(new) fields in stellar parameters: V, VSINI, GAMMA; all orbit pars except for
trend and freeze\_ecc; all transit parameters; all SE parameters;
fields for stellar properties: MSTAR, RSTAR, TEFF, RHOSTAR, LOGG, FE.

VREF is not the same as REF for J H KS, which do not have XREF
fields. See \cite{Wright2011} for references of J H KS mags -- I think
he mentioned it there.

Other general reference fields: In \cite{Wright2011}: FIRSTREF,
FIRSTURL, ORBREF, ORBURL. New: SPECREF, SPECURL contain source of most
of the spectroscopic parameters listed for convenience; actual
references in the REF fields take precedence over this one.

We now report the month when the peer-reviewed paper is accepted to
ApJ to better track of the trend in exoplanetary detections. Moreover,
we report the discovery methods for the host star and the planet
separately: STARDISCMETH and PLANETDISCMETH. See Section~ for more
details.  


%------------------------------------------------------------------------------
\subsection{Revised and Removed Fields}

These include:

OTHERNAME - This is now listed as other name of planet instead of star;
** OTHTERNAME has always been the name of the star I think...?

DISCMETH - We have replaced DISCMETH with PLANETDISCMETH and STARDISCMETH to better report how the host star and the planet are detected. 

S - changed to SHK; ZZZ What's the source for SHK and RHK? Still discovery
paper and Butler 2006? ZZZ SHK is a poorly maintained field, and it is
unreferenced at the moment though we plan to include propoer reference
in the future.

SPSTAR - stellar type of star (unvetted), gone;

NSTEDID - replaced by EANAME (Exoplanet Archive).

MASSREF, MASSURL - originally for stellar mass reference, now for planet mass.

%------------------------------------------------------------------------------
Figure: Figure of single planet page, to show updated transit
parameters and RV curves etc.?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inclusion of the Kepler Planet Candidates and Other Exoplanets on Exoplanets.org}\label{sec:kepler}

We now include \kepler\ candidates... They can be displayed by
checking the `Kepler' option for the interactive data table.

We also include robustly detected planets discovered microlensing,
imaging, timing, astrometric motion. They can be displayed by check
the `Other' option for the table. They are not included in the EOD
(especially some microlensing and imaging planets) because of poorly
characterized orbits...

Also add our criteria for vetting IMAGING planets, which can be found
here: http://exoplanets.org/methodology.html; do we have any similar
criteria for Microlensing, timing and astrometry planets? Like mass
cut etc.?

Figure: some comparison figures of Kepler candidate properties
vs. EOD planet properties, such as mass-period, mass-radius?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the Website}

Onsi? Essential updates on the website.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future}\label{sec:conclusion}

Any planned future improvements and updates?


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments

NSF funding?

SXW acknowledges support from PSARC.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References:
%\newpage
\input{references.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table
\clearpage

\begin{deluxetable}{llll}
\tabletypesize{\scriptsize}
%\rotate
\tablewidth{0pt}
\tablecaption{Fields of Exoplanet Orbit Database\label{tab:par}}
\tablehead{
  \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{b}}
}
\startdata
%
\sidehead{\textbf{Planet Information}}
NAME\dotfill & String & Name of planet & \nodata \\
OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\
COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\
HD\dotfill & Long Integer & Henry Draper number of sar & \nodata \\
HR\dotfill & Integer & Bright Star Catalog number of star & \nodata \\
HIPP\dotfill & Long Integer & \textit{Hipparcos} catalog number of
star & \nodata \\
SAO\dotfill & Long Integer & SAO catalog number of star & \nodata \\
GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata \\
BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata \\
RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  \\
DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata \\
DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
KEPID\dotfill & Long Integer & The unique \kepler\ star identifier & \nodata \\
KOI\dotfill & Float & KOI object number & \nodata \\
KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\
%
\sidehead{\textbf{Stellar Parameters}}
BMV\dotfill & Float & $B-V$ color & \nodata \\
V\dotfill & Float & $V$ magnitude & -REF,-URL \\
J\dotfill & Float & $J$ magnitude & \nodata \\
H\dotfill & Float & $H$ magnitude & \nodata \\
KS\dotfill & Float & $K_S$ magnitude & \nodata \\
DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. \\
PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
VSINI\dotfill & Float & Projected equatorial rotational velocity of
star in k\mps & -UPPER, etc. \\
GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. \\
%
\sidehead{\textbf{Orbit Parameters}}
PER\dotfill & Double & Orbital period in days & -UPPER, etc. \\
ECC\dotfill & Float & Orbital eccentricity & -UPPER, etc. \\
OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. \\
K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER, etc. \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\
I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. \\
MSINI\dotfill & Float & Minimum mass (as calculated from the mass
function) in \mjup & -UPPER, etc. \\
A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. \\
SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. \\
TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
LAMBDA\dotfill & Float & Projected spin-orbit misalignment in degrees & -UPPER, etc. \\
BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. \\
FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\
%
\sidehead{\textbf{Transit Parameters}}
DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\
TT\dotfill & Float & Epoch of transit center in
HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER, etc. \\
AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. \\
B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
DENSITY\dotfill & Float & Density of planet in g cc$^{-1}$ &
-UPPER, etc. \\
GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of planet in cgs unit &
-UPPER, etc. \\
TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\
DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. \\
RR\dotfill & Float & $(R_p/R_*)$ & -UPPER, etc. \\
%
\sidehead{\textbf{Secondary Eclipse}}
SE\dotfill & Boolean & If true, at least one secondary eclipse has
been detected & -REF,-URL \\
SEDEPTHJ\dotfill & Float & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
SEDEPTHH\dotfill & Float & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
SEDEPTHKS\dotfill & Float & Secondary eclipse depth in $K_S$
band & -UPPER, etc. \\
SEDEPTHKP\dotfill & Float & Secondary eclipse depth in the
\kepler\ photometry band & -UPPER, etc. \\
SEDEPTH36\dotfill & Float & Secondary eclipse depth in
\spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. \\
SEDEPTH45\dotfill & Float & Secondary eclipse depth in
\spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. \\
SEDEPTH58\dotfill & Float & Secondary eclipse depth in
\spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. \\
SEDEPTH80\dotfill & Float & Secondary eclipse depth in
\spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\
SET\dotfill & Double & Epoch of secondary eclipse center in
HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
%
\sidehead{\textbf{Fit \& References}}
RMS\dotfill & Float & Root-mean-square residuals to orbital RV fit & \nodata \\
CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata \\
NOBS\dotfill & Integer & Number of observations used in fit & \nodata \\
NCOMP\dotfill & Integer & Number of planetary companions known & \nodata \\
MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
FIRSTREF\dotfill & String & First peer-reviewed publication of
planetary orbit & FIRSTURL \\
ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\
%
\sidehead{\textbf{Stellar Properties}}
STAR\dotfill & String & Standard name for host star & \nodata \\
MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. \\
LOGG\dotfill & Float & Spectroscopic $\log{g}$ (surface gravity) of
host star in cgs unit & -UPPER, etc. \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata \\
SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL \\
%
\sidehead{\textbf{Links}}
JSNAME\dotfill & String & Name of host star used in the Extrasolar
Planets Encyclopaedia & EPEURL \\
ETDNAME\dotfill & String & Name of planet used in the Exoplanet
Transit Database & ETDURL \\
SIMBADNAME\dotfill & String & Valid SIMBAD name of host star (or
planet, if available) & SIMBADURL \\
EANAME\dotfill & String & Name of planet used in the Exoplanet
Archive database & EAURL \\
\enddata
\tablenotetext{a}{Fields in bold are updates or new additions from
  \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
\tablenotetext{b}{-UPPER etc. means ``-UPPER, -LOWER, U-, -REF, -URL",
where ``-" stands for the name of the field listed in the first
column. They are...}
\tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};
  changed to other commonly used name for planet.}
\tablenotetext{d}{The same as in \cite{Wright2011}, HJD/BJD etc.\ are
  still not consistent.}
\end{deluxetable}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{CJK*}

\end{document}
